---
title: ""
author: "Federico Chung, Will Madairy, Sofia Pozsonyiova, Quinn Rafferty"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    toc: true
    toc_float: true
bibliography: Library.bib
---

```{r, warning=FALSE, include=FALSE}
library(dplyr)
library(usmap)
library(maps)
library(ggplot2)
library(tidyverse)
library(ggmap)
library(viridis)
library(rgdal)
library(gridExtra)
library(plotly)
library(janitor)
library(reshape2)
library(tidyr)
library(rstan)
library(rstanarm)
library(bayesplot)
```

```{r, include=FALSE, warning=FALSE}
prediction_summary_data <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
  # Calculate summary statistics of simulated 
  # posterior predictive models for each case
  l_outer <- function(x){quantile(x, (1-prob_outer) / 2)}
  l_inner <- function(x){quantile(x, (1-prob_inner) / 2)}
  u_inner <- function(x){quantile(x, 1 - (1-prob_inner) / 2)}
  u_outer <- function(x){quantile(x, 1 - (1-prob_outer) / 2)}
  df <- data.frame(yrep) %>% 
    summarize_all(list(mean, sd, median, mad, l_outer, l_inner, u_inner, u_outer)) %>%
    unlist() %>% 
    matrix(., length(y), 8) %>% 
    data.frame()
  names(df) <- c("post_mean", "post_sd", "post_median", "post_mad", "l_outer", "l_inner", "u_inner", "u_outer")
  data.frame(cbind(y, df))
}


prediction_summary <- function(y, yrep, prob_inner = 0.5, prob_outer = 0.95){
  # This function summarizes the predictions across all cases
  pred_data <- prediction_summary_data(y, yrep, prob_inner = prob_inner, prob_outer = prob_outer) %>% 
    mutate(error = y - post_median) %>% 
    mutate(error_scaled = error / post_mad) %>% 
    mutate(within_inner = (y >= l_inner) & (y <= u_inner)) %>% 
    mutate(within_outer = (y >= l_outer) & (y <= u_outer))
  
  
  pred_summary <- pred_data %>% 
    summarize(mae = median(abs(error)), 
      mae_scaled = median(abs(error_scaled)),
      within_inner = mean(within_inner),
      within_outer = mean(within_outer)
    )
  names(pred_summary)[3] <- paste0("within_", prob_inner*100)
  names(pred_summary)[4] <- paste0("within_", prob_outer*100)
  
  pred_summary
}
```


\
\


# Introduction

Make sure to discuss the time period of interest 
## Project Motivations

## Project Goals


\
\



# Data

## Data Descriptions

## Variables of interest

## Visualizations (Quinn)

\
\



# Methods & Models (Feddy and Will)

## Markov Chain Algorithm 

## Models of Interest

## Model Descriptions

\
\


# Model Evaluation

## Model 1 Evaluation( Repeated measures)

## Model 2 Evaluation (Normal Regression)

## Model 3 Evaluation(Repeated Reg + Normal)

## Model 4 Evaluation (Longitudinal)


\
\



# Results (Will)

## Posterior Predctions All States 

### Table 

## Posterior Prediction One State

## Final Model 


\
\

# Conclusion 

## Limitations

## Future Work

\
\


# Acknowledgments and References 













